# Marvel United: Multiverse (season 3)

The only chunks that will be used from this document are `modular-setup` and `modular-processing` --- the rest will be ignored. You can control which versions of each chunk is used by changing their names in this document.

```{r modular-setup}
pdf_file <- "mu_season3_horiz_dividers.pdf, mu_horiz_update1.pdf"

# libraries needed for code in this file
library(readr)
library(dplyr)
library(tidyr)
library(stringr)

add_jpg_dividers <- function(img_files) {
  # This will be run later, in 'modular-processing',
  # but I define it here so it can be used reliably in any version below.
  # Meant to be run *before* reordering the list of image files ;)
  if (!isTRUE(params$extract_images)) {
    # Don't do anything unless image extraction was run.
    return(img_files)
  }
  # helper function to read in standalong .jpg files
  proc_jpg <- function (input, output) {
    magick::image_read(input) |> 
    magick::image_crop("541x390+1+1") |>
    magick::image_strip() |>
    magick::image_write(path = output, format = 'png')
  }
  ## Add Apocalypse (AOA) correction (standalone .jpg file)
  # and replace image #40 with the corrected image
  img_tmp <- proc_jpg('input/apocalypse.jpg', 'pdf_images/div-040.png')
  ## Add missing Void Anti-Hero Villain alt (standalone .jpg file)
  void_file <- sprintf("pdf_images/div-%03d.png", length(img_files) +1)
  img_tmp <- proc_jpg('input/void_-_vp.jpg', void_file)
  # Append to the end of the list 
  img_files <- c(img_files, void_file)
  return(img_files)
}
```

Divider index list sort order:

-   by Box (custom order, depending on what fits best)
-   Kickstarter Exclusive items grouped together at the end or beginning (in case a user is printing for a retail edition and doesn't need these, they can be on a separate page, if necessary).
-   Heroes, Villains, Anti-Heroes, [Other]
    -   Anti-Hero alts are sorted by name (Hero first, then Villain for each character): I figure those wanting to use these are grouping them by character name more than Hero / Villain; plus, it looks nice with 2 columns and each row is a character.
-   Alphabetical by name

```{r modular-processing-box}
# Add jpg dividers [Apocalypse (AOA), Void Villain alt]
img_files <- add_jpg_dividers(img_files)
# Reorder divider image files
img_files <- img_files[
  c(# Alphabetical, by box: Heroes, Villains, Anti-Hero alts, Other, KS exclusives (if retail)
    # Core Box (1:13) [13-14]
    2, 1, 10, 3, 6, 4, 5, NA, 
    12, 7:9,
    11, 13,  # Anti-Hero alts
    # Galactus (14:23) [10]
    14, 16, 
    19:20, 22, 21, 17, 23, 
    15, 18,  # Anti-Hero alts
    # Pets (184:191) [8]
    184:191,
    # Promos (87:171) [63+7+9+7=85-86]
    ## Heroes
    97:98, 91, 96, 95, 89, 94, 88, 92:93, 
    112, 114, 116, 108, 99, 172, 100, 90, 120:121, 
    124, 126, 127, 129, 131, 134, 132, 140, 142, 152, 
    154, 155, 156, 157, 162, 160, 159, 164, 166, 170, 
    ## Villains
    167, 101, 103:106, 113, 107, 115, 109, 111, 
    118:119, 102, 122, 123, 125, 128, 130, 135, 133,
    153, 141, 158, 163, 165, 169, 171, 110, 
    ## Other
    173,     # Generic Equipment (Other or Promos? Wherever fits)  
    ## Anti-Heroes
    147, 146, 145, 144, 136, 137, 138, 139, 150, 151, 149, 148, 
    168,     # Winter Guard (Villain)
    117, 143, 161,  # Winter Guard (Heroes)
    # Civil War (49:58) [10-11; 12] - missing Mission, Event, Cell, Last Player cards? (Registration Clash, Clash of Heroes)
    58, 57,  # KS Exclusives
    53, 56, 49, 54, 55, 50, 51, 52,
    239, NA, # Population cards; placeholder for "Registration Clash"?
    # Maximum Carnage (64:73) [10]
    70, 
    67, 72, 64:66, 68,
    69,      # KS Exclusive
    71, 73,  # Anti-Hero Alts
    # World War Hulk (74:87) [14-15] - missing Anti-Hero alt for The Void? (present in vertical dividers)
    78, 77, 75, 74, 79,
    86, 87, 83,  # Villain Hulk (83) is "World Breaker Hulk"
    81, 85, 80, 84, 82, 240,  # Anti-Hero alts (placeholder for The Void)
    76,      # KS Exclusive
    # Age of Apocalypse (36:42) [7]
    38, 37, 39, 36,
    40:42,   # 40 = Apocalypse, to be replaced with correction (AOA)
    # Annihilation (59:63, 174) [6]
    62, 59:61, 63, 
    174,     # Complications Challenge
    # Secret Invasion (43:48) [6]
    44, 43, 45:46,
    47:48,
    # War of Kings (24:35) [12]
    24, 26, 32, 27:28, 30, 25, 29,
    34, 31,
    33, 35,  # Anti-Hero alts
    # Team Decks (192:222, 231:238) [39]
    192,
    193, 195:198, 200, 204, 209, 211, 214:218, 222,     # Retail
    231:233, 237, 234:236, 238,                         # Promos
    194, 199, 201:203, 205:208, 210, 212:213, 219:221,  # KSE optional buy
    ## 223-230 are from the equipment card pockets page (not accurately cropped): skip
    # Campaigns (175:183) [9]
    175:183,
    # Other
    NA
  )
]
# Custom page breaks based on custom divider list above.
page_breaks <- c(13, 25) # 64, 112)
# Add Apocalypse (AOA) correction (standalone .jpg file)
img_tmp <- 
  magick::image_read('input/apocalypse.jpg') |> 
  magick::image_crop("541x390+1+1") |>
  magick::image_strip() |>
  magick::image_write(path = 'pdf_images/div-aoa.png', format = 'png')
# Replace image #40 with the corrected image (AOA)
img_files <- sub("div-040.png", "div-aoa.png", img_files)
```

## Alternate layout

-   bundle retail content together
-   then all the Kickstarter Exclusive content (in a separate file)

```{r modular-processing-retail}
# Add jpg dividers [Apocalypse (AOA), Void Villain alt]
img_files <- add_jpg_dividers(img_files)
# Reorder divider image files
img_files <- img_files[
  c(# Alphabetical, by box: Heroes, Villains, Anti-Hero alts, Other, KS exclusives (if retail)
    # Core Box (1:13) [13-14]
    2, 1, 10, 3, 6, 4, 5, NA, 12, 7:9,
    11, 13,  # Anti-Hero alts
    # Maximum Carnage (64:73) [10]
    70, 
    67, 72, 64:66, 68,
    69,      # KS Exclusive
    71, 73,  # Anti-Hero Alts
    # Civil War (49:58) [10-11; 12] - missing Mission, Event, Cell, Last Player cards? (Registration Clash, Clash of Heroes)
    53, 56, 49, 54, 55, 50, 51, 52,
    58, 57,  # KS Exclusives
    239, # NA, # Population cards; placeholder for "Registration Clash"?
    # World War Hulk (74:87) [14-15] - missing Anti-Hero alt for The Void? (present in vertical dividers)
    76,      # KS Exclusive
    78, 77, 75, 74, 79,
    86, 87, 83,  # Villain Hulk (83) is "World Breaker Hulk"
    81, 85, 80, 84, 82, 240,  # Anti-Hero alts (+ The Void Villain alt)
    # Team Decks [15-16]
    192,
    193, 195:198, 200, 204, 209, 211, 214:218, 222,     # Retail
    # Galactus (14:23) [10]
    14, 16, 
    19:20, 22, 21, 17, 23, 
    15, 18,  # Anti-Hero alts
    # Pets (184:191) [8]
    184:191,
    # Promos (87:171) [63+7+9+7=85-86]
    ## Heroes
    97:98, 91, 96, 95, 89, 94, 88, 92:93, 
    112, 114, 116, 108, 99, 172, 100, 90, 120:121, 
    124, 126, 127, 129, 131, 134, 132, 140, 142, 152, 
    154, 155, 156, 157, 162, 160, 159, 164, 166, 170, 
    ## Villains
    167, 101, 103:106, 113, 107, 115, 109, 111, 
    118:119, 102, 122, 123, 125, 128, 130, 135, 133,
    153, 141, 158, 163, 165, 169, 171, 110, 
    ## Other
    173,     # Generic Equipment (Other or Promos? Wherever fits)  
    ## Anti-Heroes
    147, 146, 145, 144, 136, 137, 138, 139, 150, 151, 149, 148, 
    168,     # Winter Guard (Villain)
    117, 143, 161,  # Winter Guard (Heroes)
    # Age of Apocalypse (36:42) [7]
    38, 37, 39, 36,
    40:42,   # 40 = Apocalypse, to be replaced with correction (AOA)
    # Annihilation (59:63, 174) [6]
    62, 59:61, 63, 
    174,     # Complications Challenge
    # Secret Invasion (43:48) [6]
    44, 43, 45:46,
    47:48,
    # War of Kings (24:35) [12]
    24, 26, 32, 27:28, 30, 25, 29,
    34, 31,
    33, 35,  # Anti-Hero alts
    # Team Decks (192:222, 231:238) [39]
    192,
    231:233, 237, 234:236, 238,                         # Promos
    194, 199, 201:203, 205:208, 210, 212:213, 219:221,  # KSE optional buy
    ## 223-230 are from the equipment card pockets page (not accurately cropped): skip
    # Campaigns (175:183) [9]
    175:183,
    # Other
    NA
  )
]
# Custom page breaks based on custom divider list above.
page_breaks <- c(13, 125, 178)
```

## Set order using external dataset

-   bundle retail content together
-   then all the Kickstarter Exclusive content (in a separate file)

The overwhelming majority of users responding to [my poll on BGG](https://boardgamegeek.com/thread/3339049/dividers-sort-order-preferences) preferred grouping by type (Heroes, Villains, etc.), so the first file posted to BGG was grouped that way.  I might make a second version sorted by box, in case it's useful for those who didn't get everything.

This is a lot of code, but was an interesting experiment. :D  

Next time, it might be simpler to just arrange the external file manually instead of all this manipulation.  Alternate sort orders can be 'saved' as indices in separate columns ('sort1', 'page.break1', 'sort2', etc.).

```{r modular-processing}
# Add jpg dividers [Apocalypse (AOA), Void Villain alt]
img_files <- add_jpg_dividers(img_files)

# Read data file with dividers information for ordering ====
div_data <- read_csv(
  'modular_code/MU3-M-data.csv', 
  na = "", 
  name_repair = function(.x) {
    .x |> vctrs::vec_as_names(repair = "universal") |> make.names(allow_ = FALSE) |> tolower()
  }
)
# Clean data
div_data <- div_data |> 
  rename(
    divider     = divider.., 
    villain.div = villain.div.., 
    ah.hero     = anti.hero..hero, 
    ah.villain  = anti.hero..villain
  ) |> 
  filter(!if_all(c(divider, villain.div, ah.hero, ah.villain), ~ is.na(.x) )) |> 
  mutate( across(villain.div:ah.villain, as.character) )
# pivot (Anti-Hero columns) to a single column with divider numbers
div_long <- div_data |> 
  pivot_longer(
    cols = divider:ah.villain,
    names_to = 'type.ah'
  ) |> 
  # cleanup: remove extra rows (Villains with values in both 'divider' and 'villain'; anything else that is NA)
  filter(
    ifelse(type == "Villain", type.ah == "divider", !is.na(value))
  ) |> 
  mutate(
    # now we can convert values to numeric, where "NA" will become true NAs again.
    value = as.numeric(value) |> suppressWarnings(),
    # cleanup anti-hero subtype labels
    type.ah = case_when(
      type != "Anti-Hero" ~ NA,
      str_starts(type.ah, "div")      ~ "hero",
      str_starts(type.ah, "villain")  ~ "villain",
      .default = type.ah
    ),
  ) |> 
  # move columns to desired locations
  relocate(type.ah, .after = type) |> 
  relocate(value, .before = page.break)

# Porcess & Sort divider data to desired order ====
sort_divs <- "by type"
if (sort_divs == "by type") {
  div_sorted <- div_long |> 
    mutate(
      # set sort order with order of levels = (don't forget any!)
      type = factor(
        type, 
        levels = c(
          "Hero", 
          "Villain", 
          "Anti-Hero", 
          "Pet", 
          "Team", 
          "Campaign", 
          "Other", 
          "Challenge"
        )
      ),
      type.ah = factor(
        type.ah, 
        levels = c("hero", "villain", "ah.hero", "ah.villain")
      ),
      # box = ifelse(type %in% c("Team", "Other"), box, NA)
      # assign alternate names to villain forms of Anti-Heroes
      name = case_when(
        type == "Anti-Hero" & str_detect(type.ah, "villain") ~ str_replace(name, "^.*\\/\\s?", ""),
        type == "Anti-Hero" & str_detect(type.ah, "hero")    ~ str_replace(name, "\\s?\\/.*$", ""),
        .default = name
      )
    ) |> 
    ## SORT
    arrange(type, type.ah, str_rank(name)) |> 
    filter(!is.na(value)) |> 
    # derive page breaks
    mutate(
      page.break = case_when(
        # type == "Villain"   & !duplicated(type)  ~ TRUE,
        type == "Anti-Hero" & !duplicated(type)  ~ TRUE,
        .default = NA
      )
    )
  
} else if (str_detect(sort_divs, "by box")) {
  # Group by box, all Retail boxes together; sort by type, then name (mostly)
  # Decided it wasn't worth grouping the KSE content from retail boxes with other KSE content.  
  # Keeping them with their boxes (but grouping retail ones together) 
  # is a nicer layout (to me), and it's only 4 extra dividers 
  # for those who purchased the retail-only versions.  Apologies for the FOMO.
  # Add "KSE" to sort_divs to group all KSE together instead.
  div_sorted <- div_long |> 
    # Insert blank dividers for spacing
    bind_rows(
      filter(div_long, 
             str_detect(box, "Core"), 
             type == "Villain"
      )[1, ] |> 
        mutate(
          name = "_ blank _",
          value = NA
        ),
      filter(div_long, 
             str_detect(box, "Carnage"), 
             type == "Anti-Hero",
             str_detect(type.ah, "ah\\.")
      )[str_detect(sort_divs, "KSE") |> as.integer( ), ] |> 
        mutate(
          name = "_ blank _",
          value = NA
        )
    ) |> 
    # duplicate "Teams" divider?  Not worth having an extra, just include it with Retail or KSE
    mutate(
      # make "Teams" divider KSE: assuming it's only really needed if you got more than the retail Team decks.
      ks.exclusive = ifelse(name == "_ Teams", 1, ks.exclusive),
      # treat "Doc Samson" as "Other" for sorting within the box (unless grouping all KSE together)
      type = ifelse(!str_detect(sort_divs, "KSE") & name == "Doc Samson", 
                    "Other", 
                    type
      ),
      # treat "Doc Samson" as part of "Civil War" for sorting with other KSE content
      box = ifelse(str_detect(sort_divs, "KSE") & name == "Doc Samson", 
                    "Civil War", 
                    box
      ),
      # Set sort order with order of levels = (don't forget any!)
      type.ah = type.ah |> 
        factor(levels = c("hero", "villain", "ah.hero", "ah.villain")),
      type = ifelse(
        type == "Anti-Hero" & !str_detect(type.ah, "^ah"), 
        paste0( toupper(substring(type.ah, 1, 1)), tolower(substring(type.ah, 2)) ), 
        type
      ) |> 
        factor(levels = c(
                 "Hero", 
                 "Villain", 
                 "Anti-Hero", # alts
                 "Pet", 
                 "Challenge",
                 "Team", 
                 "Campaign", 
                 "Other"
               )
        ),
      collection = case_when(
        type == "Team" & box != "Team Decks"   ~ "Teams",
        # Move "Generic Equipment" to end (of Campaigns) 
        # [or to blank space in front of villain dividers in Core box instead?]
        str_detect(name, "Generic Equipment") ~ "EQ",
        .default = box
      ) |> 
        factor(levels = c(
          "Multiverse Core",
          "Maximum Carnage",
          "Civil War",
          "World War Hulk",
          "Team Decks",
          ifelse(!str_detect(sort_divs, "KSE"), "The Coming of Galactus", NA), 
          "Multiverse Promos",
          "Multiverse Promos (Omniverse All-In Bonus)",
          "The Age of Apocalypse",
          ifelse(str_detect(sort_divs, "KSE"), "The Coming of Galactus", NA), 
          ifelse(str_detect(sort_divs, "KSE"), "Pets", NA), 
          "Annihilation",
          "Secret Invasion",
          "War of Kings",
          "Teams",
          "Campaigns", "EQ",
          ifelse(!str_detect(sort_divs, "KSE"), "Pets", NA)
        )
        ),
      # Ensure "Teams" divider stays in front of others
      box = ifelse(box == "Team", "_ Team", box),
      # Group Winter Guard together (Anti-Hero alts)
      name = ifelse(
        type == "Anti-Hero" & str_detect(team, "Winter Guard") & 
          name != "Winter Guard" & !is.na(team),
        paste("Winter Guard:", name),
        name
      ),
      # Move Galactus and Heralds dividers to front of their group
      name = ifelse(str_detect(name, "Galactus"), paste("_", name), name),
      # assign alternate names to villain forms of Anti-Heroes, but not alts (so they stay together)
      name = case_when(
        type == "Anti-Hero" & str_detect(type.ah, "^villain") ~ str_replace(name, "^.*\\/\\s?", ""),
        type == "Anti-Hero" & str_detect(type.ah, "^hero")    ~ str_replace(name, "\\s?\\/.*$", ""),
        .default = name
      )
    ) |> 
    ## SORT
    (\(.x)  # anonymous function for if() in a pipe sequence
     if (str_detect(sort_divs, "KSE")) {
       .x |> 
       arrange(ks.exclusive, collection, type,
               str_rank(box), str_rank(name), type.ah
       )
     } else {
       .x |> 
       arrange(collection, type, ks.exclusive, 
               str_rank(box), str_rank(name), type.ah
       )
     }
    )() |> 
    # add page breaks
    mutate(
      page.break = case_when(
        box == "Multiverse Core" & 
          type == "Anti-Hero" & 
          !duplicated(type)  ~ TRUE,
        str_detect(sort_divs, "KSE") & 
          as.logical(ks.exclusive) & !duplicated(ks.exclusive) ~ TRUE,
        !str_detect(sort_divs, "KSE") & 
          box == "The Coming of Galactus" &
          !duplicated(box) ~ TRUE,
        box == "Civil War" &
          !duplicated(box) ~ TRUE,
        box == "Annihilation" &
          !duplicated(box) ~ TRUE,
        .default = NA
      )
    )
  # derive page numbers? (increment after number of dividers per page [6] *and* at a page.break)
} else {  # Manual order - just use the same order as in the data file (notwithstanding Anti-Hero grouping)
  div_sorted <- div_long
} 

# Reorder divider image file list
img_files <- img_files[div_sorted$value]
# extract page breaks (if any)
page_breaks <- div_sorted |> 
  pull(page.break) |> 
  as.logical() |> 
  which()

```
