# Marvel United: Multiverse (season 3)

The only chunks that will be used from this document are `modular-setup` and `modular-processing` --- the rest will be ignored. You can control which versions of each chunk is used by changing their names in this document.

```{r modular-setup}
pdf_file <- "mu_season3_horiz_dividers.pdf, mu_horiz_update1.pdf"

# libraries needed for code in this file
library(readr)
library(dplyr)
library(tidyr)
library(stringr)

add_jpg_dividers <- function(img_files) {
  # This will be run later, in 'modular-processing',
  # but I define it here so it can be used reliably in any version below.
  # Meant to be run *before* reordering the list of image files ;)
  if (!isTRUE(params$extract_images)) {
    # Don't do anything unless image extraction was run.
    return(img_files)
  }
  # helper function to read in standalong .jpg files
  proc_jpg <- function (input, output) {
    magick::image_read(input) |> 
    magick::image_crop("541x390+1+1") |>
    magick::image_strip() |>
    magick::image_write(path = output, format = 'png')
  }
  ## Add Apocalypse (AOA) correction (standalone .jpg file)
  # and replace image #40 with the corrected image
  img_tmp <- proc_jpg('input/apocalypse.jpg', 'pdf_images/div-040.png')
  ## Add missing Void Anti-Hero Villain alt (standalone .jpg file)
  void_file <- sprintf("pdf_images/div-%03d.png", length(img_files) +1)
  img_tmp <- proc_jpg('input/void_-_vp.jpg', void_file)
  # Append to the end of the list 
  img_files <- c(img_files, void_file)
  return(img_files)
}
```

Divider index list sort order:

-   by Box (custom order, depending on what fits best)
-   Kickstarter Exclusive items grouped together at the end or beginning (in case a user is printing for a retail edition and doesn't need these, they can be on a separate page, if necessary).
-   Heroes, Villains, Anti-Heroes, [Other]
    -   Anti-Hero alts are sorted by name (Hero first, then Villain for each character): I figure those wanting to use these are grouping them by character name more than Hero / Villain; plus, it looks nice with 2 columns and each row is a character.
-   Alphabetical by name

```{r modular-processing-box}
# Add jpg dividers [Apocalypse (AOA), Void Villain alt]
img_files <- add_jpg_dividers(img_files)
# Reorder divider image files
img_files <- img_files[
  c(# Alphabetical, by box: Heroes, Villains, Anti-Hero alts, Other, KS exclusives (if retail)
    # Core Box (1:13) [13-14]
    2, 1, 10, 3, 6, 4, 5, NA, 
    12, 7:9,
    11, 13,  # Anti-Hero alts
    # Galactus (14:23) [10]
    14, 16, 
    19:20, 22, 21, 17, 23, 
    15, 18,  # Anti-Hero alts
    # Pets (184:191) [8]
    184:191,
    # Promos (87:171) [63+7+9+7=85-86]
    ## Heroes
    97:98, 91, 96, 95, 89, 94, 88, 92:93, 
    112, 114, 116, 108, 99, 172, 100, 90, 120:121, 
    124, 126, 127, 129, 131, 134, 132, 140, 142, 152, 
    154, 155, 156, 157, 162, 160, 159, 164, 166, 170, 
    ## Villains
    167, 101, 103:106, 113, 107, 115, 109, 111, 
    118:119, 102, 122, 123, 125, 128, 130, 135, 133,
    153, 141, 158, 163, 165, 169, 171, 110, 
    ## Other
    173,     # Generic Equipment (Other or Promos? Wherever fits)  
    ## Anti-Heroes
    147, 146, 145, 144, 136, 137, 138, 139, 150, 151, 149, 148, 
    168,     # Winter Guard (Villain)
    117, 143, 161,  # Winter Guard (Heroes)
    # Civil War (49:58) [10-11; 12] - missing Mission, Event, Cell, Last Player cards? (Registration Clash, Clash of Heroes)
    58, 57,  # KS Exclusives
    53, 56, 49, 54, 55, 50, 51, 52,
    239, NA, # Population cards; placeholder for "Registration Clash"?
    # Maximum Carnage (64:73) [10]
    70, 
    67, 72, 64:66, 68,
    69,      # KS Exclusive
    71, 73,  # Anti-Hero Alts
    # World War Hulk (74:87) [14-15] - missing Anti-Hero alt for The Void? (present in vertical dividers)
    78, 77, 75, 74, 79,
    86, 87, 83,  # Villain Hulk (83) is "World Breaker Hulk"
    81, 85, 80, 84, 82, 240,  # Anti-Hero alts (placeholder for The Void)
    76,      # KS Exclusive
    # Age of Apocalypse (36:42) [7]
    38, 37, 39, 36,
    40:42,   # 40 = Apocalypse, to be replaced with correction (AOA)
    # Annihilation (59:63, 174) [6]
    62, 59:61, 63, 
    174,     # Complications Challenge
    # Secret Invasion (43:48) [6]
    44, 43, 45:46,
    47:48,
    # War of Kings (24:35) [12]
    24, 26, 32, 27:28, 30, 25, 29,
    34, 31,
    33, 35,  # Anti-Hero alts
    # Team Decks (192:222, 231:238) [39]
    192,
    193, 195:198, 200, 204, 209, 211, 214:218, 222,     # Retail
    231:233, 237, 234:236, 238,                         # Promos
    194, 199, 201:203, 205:208, 210, 212:213, 219:221,  # KSE optional buy
    ## 223-230 are from the equipment card pockets page (not accurately cropped): skip
    # Campaigns (175:183) [9]
    175:183,
    # Other
    NA
  )
]
# Custom page breaks based on custom divider list above.
page_breaks <- c(13, 25) # 64, 112)
# Add Apocalypse (AOA) correction (standalone .jpg file)
img_tmp <- 
  magick::image_read('input/apocalypse.jpg') |> 
  magick::image_crop("541x390+1+1") |>
  magick::image_strip() |>
  magick::image_write(path = 'pdf_images/div-aoa.png', format = 'png')
# Replace image #40 with the corrected image (AOA)
img_files <- sub("div-040.png", "div-aoa.png", img_files)
```

## Set order using external dataset

- By box; Heroes, Villains, Other; Alphabetical by Name
- no Anti-Hero alts (purple dividers)

```{r modular-processing}
# Add jpg dividers [Apocalypse (AOA), Void Villain alt]
img_files <- add_jpg_dividers(img_files)

# Read data file with dividers information for ordering ====
div_data <- read_csv(
  'modular_code/MU3-M-data.csv', 
  na = "", 
  name_repair = function(.x) {
    .x |> vctrs::vec_as_names(repair = "universal") |> make.names(allow_ = FALSE) |> tolower()
  }
)
# Clean data
div_data <- div_data |> 
  rename(
    divider     = divider.., 
    villain.div = villain.div.., 
    ah.hero     = anti.hero..hero, 
    ah.villain  = anti.hero..villain
  ) |> 
  filter(!if_all(c(divider, villain.div, ah.hero, ah.villain), ~ is.na(.x) )) |> 
  mutate( across(villain.div:ah.villain, as.character) )
# pivot (Anti-Hero columns) to a single column with divider numbers
div_long <- div_data |> 
  pivot_longer(
    cols = divider:ah.villain,
    names_to = 'type.ah'
  ) |> 
  # cleanup: remove extra rows (Villains with values in both 'divider' and 'villain'; anything else that is NA)
  filter(
    ifelse(type == "Villain", type.ah == "divider", !is.na(value))
  ) |> 
  mutate(
    # now we can convert values to numeric, where "NA" will become true NAs again.
    value = as.numeric(value) |> suppressWarnings(),
    # cleanup anti-hero subtype labels
    type.ah = case_when(
      type != "Anti-Hero" ~ NA,
      str_starts(type.ah, "div")      ~ "hero",
      str_starts(type.ah, "villain")  ~ "villain",
      .default = type.ah
    ),
  ) |> 
  # move columns to desired locations
  relocate(type.ah, .after = type) |> 
  relocate(value, .before = page.break)
# Filter out content I don't want to print
div_long <- div_long |> 
  filter(
    !(box %in% c(
      "The Coming of Galactus",
      "Multiverse Promos (Omniverse All-In Bonus)",
      "World War Hulk",
      "Maximum Carnage",
      "Campaigns"
    )),
    is.na(type.ah) | str_starts(type.ah, "ah\\.", neg = TRUE)
  )

# Process & Sort divider data to desired order ====
sort_divs <- "by box"
if (str_detect(sort_divs, "by box")) {
  # Group by box; sort by type, then name (mostly)
  div_sorted <- div_long |> 
    # Insert blank dividers for spacing
    # bind_rows(
    #   filter(div_long, 
    #          str_detect(box, "Core"), 
    #          type == "Villain"
    #   )[1, ] |> 
    #     mutate(
    #       name = "_ blank _",
    #       value = NA
    #     )
    # ) |> 
    mutate(
      # make "Teams" divider KSE: assuming it's only really needed if you got more than the retail Team decks.
      ks.exclusive = ifelse(name == "_ Teams", 1, ks.exclusive),
      # Set sort order with order of levels = (don't forget any!)
      type.ah = type.ah |> 
        factor(levels = c("hero", "villain", "ah.hero", "ah.villain")),
      type = ifelse(
        type == "Anti-Hero" & !str_detect(type.ah, "^ah"), 
        paste0( toupper(substring(type.ah, 1, 1)), tolower(substring(type.ah, 2)) ), 
        type
      ) |> 
        factor(levels = c(
                 "Hero", 
                 "Villain", 
                 "Anti-Hero", # alts
                 "Pet", 
                 "Challenge",
                 "Team", 
                 "Campaign", 
                 "Other"
               )
        ),
      collection = case_when(
        type == "Team" & box != "Team Decks"   ~ "Teams",
        # Move "Generic Equipment" to end (of Campaigns) 
        # [or to blank space in front of villain dividers in Core box instead?]
        str_detect(name, "Generic Equipment") ~ "EQ",
        .default = box
      ) |> 
        factor(levels = c(
          "EQ", "Multiverse Core", 
          "Civil War",
          "Multiverse Promos",
          "The Age of Apocalypse",
          "Team Decks",
          "Annihilation",
          "Secret Invasion",
          "War of Kings",
          "Pets",
          "Teams"
        )
        ),
      # Ensure "Teams" divider stays in front of others
      box = ifelse(box == "Team", "_ Team", box),
      # assign alternate names to villain forms of Anti-Heroes, but not alts (so they stay together)
      name = case_when(
        type == "Anti-Hero" & str_detect(type.ah, "^villain") ~ str_replace(name, "^.*\\/\\s?", ""),
        type == "Anti-Hero" & str_detect(type.ah, "^hero")    ~ str_replace(name, "\\s?\\/.*$", ""),
        .default = name
      )
    ) |> 
    ## SORT
    arrange(collection, type, ks.exclusive, 
            str_rank(box), str_rank(name), type.ah
    ) |> 
    # add page breaks
    mutate(
      page.break = case_when(
        box == "Multiverse Core" & 
          type == "Anti-Hero" & 
          !duplicated(type)  ~ TRUE,
        box == "Civil War" &
          !duplicated(box) ~ TRUE,
        box == "Annihilation" &
          !duplicated(box) ~ TRUE,
        .default = NA
      )
    )
  # derive page numbers? (increment after number of dividers per page [6] *and* at a page.break)
} else {  # Manual order - just use the same order as in the data file (notwithstanding Anti-Hero grouping)
  div_sorted <- div_long
} 

# Reorder divider image file list
img_files <- img_files[div_sorted$value]
# extract page breaks (if any)
page_breaks <- div_sorted |> 
  pull(page.break) |> 
  as.logical() |> 
  which()

```
