---
title: "Colour Profiles Notebook"
output: html_notebook
---

# Introduction

This file is not intended to be compiled to output --- it is more of a notebook to keep track of commands and operations I have tried, and results, as notes. It is based on `Notes.md`, but with commands that can be executed directly from the document in RStudio.

Eventually, I might combine some of this with `tests_color_profiles.Rmd`, to standardize the production of test files, and print them, in a reproducible way. Then, I might be able to clean up some of the test files that are accumulating.

The focus of this document is on color profiles, and how different steps affect them, and the results – when viewed on screen and especially when printed.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tools

-   pdfimages (part of [Poppler](https://poppler.freedesktop.org/) [utils](https://en.wikipedia.org/wiki/Poppler_(software))) to extract images from pdfs

    -   [pdfimager](https://sckott.github.io/pdfimager/) package for R interface

-   [ImageMagick](https://imagemagick.org/) to manipulate images programmatically

    -   [magick](https://docs.ropensci.org/magick/index.html) package for R interface

-   [Preview](https://support.apple.com/en-ca/guide/preview/welcome/mac) (macOS) to preview and explore images - some manual editing, mostly to test things and improve my understanding.

# PDF Information

```{zsh}
pdfinfo '../input/mu_card_dividers_v2.pdf'
```

```{zsh}
pdfinfo '../input/mu_x-men_horiz_dividers.pdf'
```

How to find out what icc color profile is embedded / tagged in a pdf file itself?

Or in the embedded images (if any or different from document)?

# Extracting images

## pdfimages {data-link="pdfimages"}

-   "-all" option extracts the image in its native format: <https://askubuntu.com/questions/776679/why-are-the-images-produced-by-pdfimages-different-when-using-the-all-flag>
    -   "-all" is equivalent to `-png -tiff -j -jp2 -jbig2 -ccitt`
-   most tutorials recommend "-png"
    -   the result appears to be the same as "-all" for the classic set (MU season 1), but X-Men (and Multiverse) is all `.jpg`.
-   with the `-j` (or `-jp2`) flag, non-jpeg images are exported to `.ppm` (colour), or `.pbm` (monochrome) - this is the case for the season 1 pdf
    -   <https://askubuntu.com/questions/150100/extracting-embedded-images-from-a-pdf>

```{zsh}
# MU season 1
pdfimages -all -f 1 -l 1 -print-filenames '../input/mu_card_dividers_v2.pdf' '../pdf_images/tests/mu1'
pdfimages -j -f 1 -l 1 -print-filenames '../input/mu_card_dividers_v2.pdf' '../pdf_images/tests/mu1-j'
pdfimages -jp2 -f 1 -l 1 -print-filenames '../input/mu_card_dividers_v2.pdf' '../pdf_images/tests/mu1-jp2'

# MU: X-Men
pdfimages -all -f 1 -l 1 -print-filenames '../input/mu_x-men_horiz_dividers.pdf' '../pdf_images/tests/mux'
pdfimages -j -f 1 -l 1 -print-filenames '../input/mu_x-men_horiz_dividers.pdf' '../pdf_images/tests/mux-j'
pdfimages -png -f 1 -l 1 -print-filenames '../input/mu_x-men_horiz_dividers.pdf' '../pdf_images/tests/mux-png'

```

Some options don't affect the output - cleanup extra files:

```{bash}
cmp '../pdf_images/tests/mu1-j-000.ppm' '../pdf_images/tests/mu1-jp2-000.ppm'
status=$?  # capture the exit status
# https://stackoverflow.com/questions/36313216/why-is-testing-to-see-if-a-command-succeeded-or-not-an-anti-pattern
if [ $status = 0 ]; then
  # if no output, the files are identical!
  echo "The files are identical!"
  rm '../pdf_images/tests/mu1-jp2-000.ppm'
  echo "../pdf_images/tests/mu1-jp2-000.ppm deleted"
fi
```

```{bash}
cmp ../pdf_images/tests/mux-000.jpg ../pdf_images/tests/mux-j-000.jpg 
status=$?  # capture the exit status
if [ $status = 0 ]; then
  echo "The files are identical!"
  rm  ../pdf_images/tests/mux-j-000.jpg
  echo "../pdf_images/tests/mux-j-000.jpg deleted"
fi
```

## pdftocairo

-   doesn't extact images, so much as convert pages to graphics formats.

-   I am curious what color profile is included in these exported files.

```{bash}
pdftocairo -png -f 1 -l 1 '../input/mu_card_dividers_v2.pdf' '../pdf_images/tests/mu1-pdftocairo'
pdftocairo -png -f 1 -l 1 '../input/mu_x-men_horiz_dividers.pdf' '../pdf_images/tests/mux-pdftocairo'
```

```{bash}
identify -verbose '../pdf_images/tests/mu1-pdftocairo-01.png'
```

```{bash}
identify -verbose '../pdf_images/tests/mux-pdftocairo-01.png'
```

# Manipulating images

## ImageMagick

<https://imagemagick.org/>

```         
brew install imagemagick
```

Get information about an image file:

```         
identify -verbose 'path/to/file'
```

Output of interest:

-   Colorspace
-   Properties
    -   "icc: ..."

### MU file information

Use ImageMagick to look at information and details about files extracted from the MU season 1 dividers pdf (see [pdfimages]):

```{bash}
identify -verbose '../pdf_images/tests/mu1-000.png'
```

```{bash}
identify -verbose '../pdf_images/tests/mu1-j-000.ppm'
```

-   Neither file has an icc color profile, according to Imagemagick

-   But Preview does show a "ColorSync profile: **sRGB IEC61966-2.1**" *for the `ppm` (jpeg) files*, but not for the png file.

    -   The Finder shows the same information under "Color profile"

The `identify` command works on pdf files, too, but provides information on each image in the pdf:

```{bash}
identify '../input/mu_card_dividers_v2.pdf'
```

No icc color profile found:

```{r}
cmd_out <- system("identify -verbose '../input/mu_card_dividers_v2.pdf'", intern = TRUE)
grep("icc", cmd_out, ignore.case = TRUE, value = TRUE)
grep("profile", cmd_out, ignore.case = TRUE, value = TRUE)
grep("iec", cmd_out, ignore.case = TRUE, value = TRUE)
```

### MU: X-Men files (jpg instead of png)

Still no color profile apparent in pdf files:

```{r}
if (F) {
  cmd_out <- system("identify -verbose '../input/mu_x-men_horiz_dividers.pdf'", intern = TRUE)
} else {
  # fewer pages, but expected to be similar (produced soon after the main file):
  cmd_out <- system("identify -verbose '../input/mu_x-men_horiz_dividers_legion.pdf'", intern = TRUE)
}
grep("icc", cmd_out, ignore.case = TRUE, value = TRUE)
grep("profile", cmd_out, ignore.case = TRUE, value = TRUE)
grep("iec", cmd_out, ignore.case = TRUE, value = TRUE)
# cat(paste(cmd_out, collapse = "\n"))
```

... unless the "Profile-xmp" entry is the color profile (just not an ICC profile)?

Examine images extracted by `pdfimages`:

```{bash}
identify -verbose ../pdf_images/tests/mux-000.jpg
```

```{bash}
identify -verbose ../pdf_images/tests/mux-png-000.png
```

-   `png` files do not seem to have icc color profiles, but the `jpg` files do!

-   The color profile showing in the MUX `jpg` files appears to be the same one that Preview finds in the `ppm` exported from the MU season 1 pdf.

This file was exported manually from Preview to `png` (File \> Export ..., choose "PNG" as output format), and includes the color profile "Adobe RGB (1998)":

```{bash}
identify -verbose '../pdf_images/tests/mu_card_dividers_v2 (Preview-Adobe).png'
```

-   Where did Preview get this color profile? Was it tagged in the original pdf, but not the embedded `png` images? Was it an assumption?

## ImageMagick & color profiles

Extract the icc color profile from a file (formerly `convert`):

```{bash}
# FAIL:
magick ../input/mu_card_dividers_v2.pdf ../pdf_images/tests/mu1-pdf.icc
magick ../pdf_images/tests/mu1-j-000.ppm ../pdf_images/tests/mu1-ppm.icc
# SUCCESS:
magick ../pdf_images/tests/mux-000.jpg ../pdf_images/tests/mux-IEC61966-2_1.icc
magick '../pdf_images/tests/mu_card_dividers_v2 (Preview-Adobe).png' ../pdf_images/tests/mu1-Adobe1998.icc
```

Compare extracted profiles with system profiles:

```{bash}
cmp '../pdf_images/tests/mux-IEC61966-2_1.icc' '/System/Library/ColorSync/Profiles/sRGB Profile.icc'
identify '../pdf_images/tests/mux-IEC61966-2_1.icc'
identify '/System/Library/ColorSync/Profiles/sRGB Profile.icc'
diff <(identify -verbose '../pdf_images/tests/mux-IEC61966-2_1.icc') <(identify -verbose '/System/Library/ColorSync/Profiles/sRGB Profile.icc')
```

Only differ in terms of creation and modification dates, as expected. Not sure what "pixels per second" is.

```{bash}
cmp '../pdf_images/tests/mu1-Adobe1998.icc' '/System/Library/ColorSync/Profiles/AdobeRGB1998.icc'
diff <(identify -verbose '../pdf_images/tests/mu1-Adobe1998.icc') <(identify -verbose '/System/Library/ColorSync/Profiles/AdobeRGB1998.icc')
```

Different file size and copyright information (!), but otherwise similar.

Add a color profile to an image - this might actually convert colors from the existing (or assumed if missing) color profile to the new one, which would change the color values:

```{bash}
magick ../pdf_images/tests/mu1-000.png -profile ../pdf_images/tests/mu1-Adobe1998.icc ../pdf_images/tests/mu1-000+adobe.png
magick ../pdf_images/tests/mu1-000.png -profile ../pdf_images/tests/mux-IEC61966-2_1.icc ../pdf_images/tests/mu1-000+iec61966.png

magick ../pdf_images/tests/mux-000.jpg -profile ../pdf_images/tests/mu1-Adobe1998.icc ../pdf_images/tests/mux-000+adobe.jpg
magick ../pdf_images/tests/mux-png-000.png -profile ../pdf_images/tests/mu1-Adobe1998.icc ../pdf_images/tests/mux-png-000+adobe.png
magick ../pdf_images/tests/mux-png-000.png -profile ../pdf_images/tests/mux-IEC61966-2_1.icc ../pdf_images/tests/mux-png-000+iec61966.png

echo $?  # output to confirm if the above succeeded.
```

<https://stackoverflow.com/questions/29633390/apply-and-remove-color-profile-with-image-magick>

Based on the documentation, I probably want to add `-strip`?

# Tests & Comparisons

I can't even seem to reproduce colours on my printer from early tests with the same file (might have been a different computer). So confusing. :(

| file                          | color profile | based on original file        | treatment                            | results - screen | results - print | Notes     |
|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
| input/mu_card_dividers_v2.pdf | ?             | \-                            | \-                                   | baseline         | baseline        | reference |
|                               |               | input/mu_card_dividers_v2.pdf | extracted image - native             |                  |                 |           |
|                               |               |                               | extracted image - other (ppm or png) |                  |                 |           |
|                               |               |                               | +Adobe 1998                          |                  |                 |           |
|                               |               |                               | +IEC                                 |                  |                 |           |
|                               |               |                               |                                      |                  |                 |           |

A table might be too wide for all the information I want to gather. I might consider a list format instead, or for more details (in addition to a summary table).
